---
title: "Assignment 2"
---

# Assignment 2

```{r}
library(tidyverse) # for everything :)
library(rvest) # for HTML scraping
library(stringr) # for string processing

# Define the URL to scrape
url <- "https://m.imdb.com/search/title/?title_type=feature&release_date=2011-01-01,2023-12-31&sort=moviemeter,desc&num_votes=2499,&countries=TR&count=250"  # Replace with the actual URL you want to scrape
url2 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=,2010-12-31&sort=moviemeter,desc&num_votes=2500,&countries=TR&count=250"




# Use read_html() to read the HTML content from the URL
html_content <- read_html(url)
html_content2 <- read_html(url2)

 
# extract titles (movie names) ++
title_names <- html_content |> html_nodes('.ipc-title__text')
title_names <- html_text(title_names)
title_names <- tail(head(title_names,-1),-1)
title_names <- str_split(title_names, " ", n=2)
title_names <- unlist(lapply(title_names, function(x) {x[2]}))
#==================================================================
title_names2 <- html_content2 |> html_nodes('.ipc-title__text')
title_names2 <- html_text(title_names2)
title_names2 <- tail(head(title_names2,-1),-1)
title_names2 <- str_split(title_names2, " ", n=2)
title_names2 <- unlist(lapply(title_names2, function(x) {x[2]}))

title <- unlist(c(title_names, title_names2))



# extract years ++
year <- html_content |> html_nodes('.sc-43986a27-8.jHYIIK.dli-title-metadata-item:nth-child(1)')
year <- html_text(year)
convert_to_numeric <- function(x) {
  ifelse(grepl("k$", x), as.numeric(sub("k$", "", x)) * 1000, as.numeric(x))
}
year <- sapply(year, convert_to_numeric)
#=================================================================================================
year2 <- html_content2 |> html_nodes('.sc-43986a27-8.jHYIIK.dli-title-metadata-item:nth-child(1)')
year2 <- html_text(year2)
convert_to_numeric <- function(x) {
  ifelse(grepl("k$", x), as.numeric(sub("k$", "", x)) * 1000, as.numeric(x))
}
year2 <- sapply(year2, convert_to_numeric)

release <- unlist(c(year, year2))

# extract the vote counts ++
votes <- html_content |> html_nodes('.sc-53c98e73-0.kRnqtn')
votes <- html_text(votes)
votes <- as.numeric(gsub("[^0-9]", "", votes))
#=================================================================================================
votes2 <- html_content2 |> html_nodes('.sc-53c98e73-0.kRnqtn')
votes2 <- html_text(votes2)
votes2 <- as.numeric(gsub("[^0-9]", "", votes2))


vote <- unlist(c(votes, votes2))


# extract the durations ++
duration <- html_content |> html_nodes('.sc-43986a27-8.jHYIIK.dli-title-metadata-item:nth-child(2)')
duration <- html_text(duration)
hours <- as.numeric(str_extract(duration, "\\d+(?=h)"))
hours[is.na(hours)] <- 0
minutes <- as.numeric(str_extract(duration, "\\d+(?=m)"))
minutes[is.na(minutes)] <- 0
total_minutes <- hours * 60 + minutes
#=================================================================================================
duration2 <- html_content2 |> html_nodes('.sc-43986a27-8.jHYIIK.dli-title-metadata-item:nth-child(2)')
duration2 <- html_text(duration2)
hours2 <- as.numeric(str_extract(duration2, "\\d+(?=h)"))
hours2[is.na(hours2)] <- 0
minutes2 <- as.numeric(str_extract(duration2, "\\d+(?=m)"))
minutes2[is.na(minutes2)] <- 0
total_minutes2 <- hours2 * 60 + minutes2


total_time <- unlist(c(total_minutes, total_minutes2))



rating <- html_content |> html_nodes('.ratingGroup--imdb-rating')
rating <- html_text(rating)
rating <- str_extract(rating, "\\d+\\.\\d+") %>%as.numeric()
#=================================================================================================
rating2 <- html_content2 |> html_nodes('.ratingGroup--imdb-rating')
rating2 <- html_text(rating2)
rating2 <- str_extract(rating2, "\\d+\\.\\d+") %>%as.numeric()


ratings <- unlist(c(rating, rating2))

#DataFrame <- merge(title, release,vote, total_time, ratings)


DataFrame <- bind_cols(
  
  MovieTitle=title,
  Release=release,
  Rating = ratings,
  Votes = vote,
  Duration=total_time
  
)
```


Question 3
a)
```{r}
DataFrame <- arrange(DataFrame,desc(Rating))
print(head(DataFrame))
print(tail(DataFrame))
```

To be honest I'm not much of a movie guy so I didn't watch any of this films, but
I've seen the trailers of the "Cumali Ceber" series and I think this movies would have worse ratings if it was possible

c)
```{r}

{r}
library(ggplot2)
# Calculate yearly rating averages
rating_avg_by_year <- DataFrame %>%
  group_by(Release) %>%
  summarise(avg_rating = mean(Rating),
            num_movies = n())

ggplot(rating_avg_by_year, aes(x = Release, y = avg_rating)) +
  geom_point() +
  labs(title = "Scatter Plot of Average Ratings of Turkish Movies Over the Years",
       x = "Year",
       y = "Average Rating") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

This graph shows a significant decline in movie ratings over the years.

```{r}

ggplot(DataFrame, aes(x = as.factor(Release), y = Rating)) + 
  geom_boxplot() +
  labs(x = "Year",
      y = "Ratings")+ ggtitle("Yearly Ratings")+
  theme(axis.text.x = element_text(angle = 90, hjust=1))

```

On the contrary, upon examining this table, it is evident that the median of the ratings over the years has remained relatively stable. Additionally, there is a notable presence of high-quality movies in recent years. This observation could be indicative of a decrease in the cost of filmmaking with the advancement of technology. Nowadays, anyone can produce a film with just an iPhone and a basic computer. However, this accessibility might lead to the production of a larger number of lower-quality movies, contributing to a decline in the overall average of film ratings.